Consistency scores in text data

### 2020-07-30 outputs/documents/paper.Rmd
Language models and Word embedding models

## Word Embedding Models
Moved from statistical to neural network. Word embedding models works by representing words as numerical dense vectors so the neural networks can understand and process. Representing words as dense vectors has a long history, but the first neural network language model was proposed in 2013 by @bengio2003neural, and became the pioneer in word embedding models. In the work of @bengio2003neural, word embedding works by encoding the words into a feature vector. The feature vector represents different aspects of the word and each word is associated with a point in a vector space.

The words that are similar will have similar representations in a vector space. The similarity of the words, however, does not depend on their spelling or forms, but by their co-occurrence in given contexts. For example, a "cat" is more similar to a "dog" instead of a "car" because we are more likely to talk about cats and dogs in a same conversation. Therefore, the co-occurrence of "cat" and "dog" has higher probability than the co-occurrence of "cat" and a "car". In other words, the distributed representation is learned by the usage of words. This permits words that are used in similar contexts to result in having similar vector representations and their semantic meanings are captured naturally.

>>>>

## Word Embedding Models
Turning words into numeric representations is an important step for machine to understand and process words. The most basic way to turn a word into a vector. However, in one-hot encoding, the number of dimensions depends on the size of the vocabulary in a given corpus, and can easily grow to extremely large. Word embedding models works by representing words as numerical dense vectors so the dimensions are reduced by representing the words by features **(Keli add citation)**. Representing words as dense vectors has a long history. but the idea of a dense embedding space for words was first explored in 2003 by @bengio2003neural, and became the prominent driver for word embedding models. In the work of @bengio2003neural, word embedding works by encoding the words into feature vectors. The feature vector represents different aspects of the word and each word is associated with a point in a vector space. The words that are similar will have similar representations in a vector space. The similarity of the words, however, does not depend on their spelling or forms, but by their co-occurrence in given contexts. For example, a "cat" is more similar to a "dog" instead of a "car" because we are more likely to talk about cats and dogs in a same conversation. Therefore, the co-occurrence of "cat" and "dog" has higher probability than the co-occurrence of "cat" and a "car". In other words, the distributed representation is learned by the usage of words. This permits words that are used in similar contexts to result in having similar vector representations and their semantic meanings are captured naturally.
